Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-11 papers/marlowe2019/paper.tex
Remove typo
Fix

Marlowe is specified by a reference semantics f or the language written in Haskell, and we can use that in a number of ways. We can interpret Marlowe contracts in Haskell itself, but we can also use that implementation, compiled into Plutus~\cite{PlutusPlatform}, to interpret Marlowe directly on the Cardano blockchain, see Section \ref{sec:implementation}. We can also execute the semantics -- translated into PureScript -- directly in a browser, to give an interactive simulation environment, see Section~\ref{sec:playground}.

@@

In the following section, we explain how we worked around these limitations and give an overview of how we use SBV to avoid runtime problems with Marlowe contracts.

\subsubsection{Using SBV to analyse Marlowe Contracts}

>>>>

Marlowe is specified by a reference semantics for the language written in Haskell, and we can use that in a number of ways. We can interpret Marlowe contracts in Haskell itself, but we can also use that implementation, compiled into Plutus~\cite{PlutusPlatform}, to interpret Marlowe directly on the Cardano blockchain, see Section \ref{sec:implementation}. We can also execute the semantics -- translated into PureScript -- directly in a browser, to give an interactive simulation environment, see Section~\ref{sec:playground}.

@@

In the following sections, we explain how we worked around these limitations and give an overview of how we use SBV to avoid runtime problems with Marlowe contracts.

\subsection{Using SBV to analyse Marlowe Contracts}
